### 2020-11-17 thesis/appendix_1.tex
same

\begin{figure}[h!]
\makebox[\textwidth]{
  \includegraphics[width=1.3\textwidth]{thesis/figures/scenario_45_compare.png}
}
  \caption[Map of Montérégie at the beginning of the Corridor protection scenario in 2010, and at the end in 2100 (baseline climate scenario)]{Map of Montérégie at the beginning of the Corridor protection scenario in 2010, and at the end of the simulation in 2100 (under baseline climate scenario).}
 \label{fig:Corr_compare}
\end{figure}

\begin{figure}[h!]
\makebox[\textwidth]{
  \includegraphics[width=1.3\textwidth]{thesis/figures/scenario_48_compare.png}
}
  \caption[Map of Montérégie at the beginning of the Corridor protection + Reforestation scenario in 2010, and at the end in 2100 (baseline climate scenario)]{Map of Montérégie at the beginning of the Corridor protection + Reforestation scenario in 2010, and at the end of the simulation in 2100 (under baseline climate scenario).}
 \label{fig:	CorrRef_compare}
\end{figure}

\begin{figure}[h!]
\makebox[\textwidth]{
  \includegraphics[width=1.3\textwidth]{thesis/figures/scenario_51_compare.png}
}
  \caption[Map of Montérégie at the beginning of the Corridor protection + Targeted Reforestation scenario in 2010, and at the end in 2100 (baseline climate scenario)]{Map of Montérégie at the beginning of the Corridor protection + Targeted Reforestation scenario in 2010, and at the end of the simulation in 2100 (under baseline climate scenario).}
 \label{fig:	CorrRefT_compare}
\end{figure}

>>>>

\begin{figure}[h!]
\makebox[\textwidth]{
  \includegraphics[width=1.3\textwidth]{thesis/figures/scenario_45_compare.png}
}
  \caption[Map of Montérégie at the beginning of the Corridor protection scenario in 2010, and at the end in 2100 (baseline climate)]{Map of Montérégie at the beginning of the Corridor protection scenario in 2010, and at the end of the simulation in 2100 (under baseline climate scenario).}
 \label{fig:Corr_compare}
\end{figure}

\begin{figure}[h!]
\makebox[\textwidth]{
  \includegraphics[width=1.3\textwidth]{thesis/figures/scenario_48_compare.png}
}
  \caption[Map of Montérégie at the beginning of the Corridor protection + Reforestation scenario in 2010, and at the end in 2100 (baseline climate)]{Map of Montérégie at the beginning of the Corridor protection + Reforestation scenario in 2010, and at the end of the simulation in 2100 (under baseline climate scenario).}
 \label{fig:	CorrRef_compare}
\end{figure}

\begin{figure}[h!]
\makebox[\textwidth]{
  \includegraphics[width=1.3\textwidth]{thesis/figures/scenario_51_compare.png}
}
  \caption[Map of Montérégie at the beginning of the Corridor protection + Targeted Reforestation scenario in 2010, and at the end in 2100 (baseline climate)]{Map of Montérégie at the beginning of the Corridor protection + Targeted Reforestation scenario in 2010, and at the end of the simulation in 2100 (under baseline climate scenario).}
 \label{fig:	CorrRefT_compare}
\end{figure}
